Incentivizing Exploration with Unbiased History

### 2018-10-23 3level.tex
leveling

\section{3-level Recommendation Policy}
Now we demonstrate how to design a policy to incentivize adaptive
exploration and improve on the $O(T^{2/3})$ regret rate. For
simplicity, we assume there are only 2 arms.

>>>>

\section{3-level Adaptive Policy}
\label{sec:3level}
Now we demonstrate how to design a e-level policy to incentivize
adaptive exploration and improve on the $O(T^{2/3})$ regret rate. In
\Cref{sec:llevel}, we will show how to extend this idea to achieve a
regret rate of $\tilde O(T^{1/2})$. For simplicity, we will focus on
the setting with 2 arms.
